Systematic studies of correlations between different order flow harmonics in Pb--Pb collisions at $\mathbf{\sqrt{s_{\rm NN}}}$ = 2.76 TeV

### 2017-08-21 appendix.tex

% !TEX root = paper.tex
\appendix
\section{Model Comparisons of the Individual Flow Harmonics $v_n$}
\label{sec:vn}
As discussed in Sec.~\ref{sec:method}, NSC$(m,n)$ is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$ but SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual harmonics $v_{n}$. Therefore, it is important to check how well the theoretical models used in Sec.~\ref{sec:theory} describe the measured $v_n$ data shown in Sec.~\ref{sec:results}. The $v_n$ is measured for charged particles in the pseudorapidity range $|\eta| < 0.8$ and the transverse momentum range $0.2 < p_{\rm T} < 5.0$ GeV/$c$ as a function of collision centrality~\cite{Adam:2016izf}.
%The comparisons are made only up to $v_4$ because model calculations are not available for $v_5$ at this moment.

>>>>

% !TEX root = paper.tex
\appendix
\section{Model Comparisons of the Individual Flow Harmonics $v_n$}
\label{sec:vn}
As discussed in Sec.~\ref{sec:method}, NSC$(m,n)$ is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$ but SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual harmonics $v_{n}$. Therefore, it is important to check how well the theoretical models used in Sec.~\ref{sec:theory} describe the measured $v_n$ data shown in Sec.~\ref{sec:results}. $v_n$ results presented in this section are for charged particles in the pseudorapidity range $|\eta| < 0.8$ and the transverse momentum range $0.2 < p_{\rm T} < 5.0$ GeV/$c$ as a function of collision centrality~\cite{Adam:2016izf}.
%The comparisons are made only up to $v_4$ because model calculations are not available for $v_5$ at this moment.

### 2017-08-21 paper.tex
putting pic version for test
add working pic version
add sami's comment
final for IRC2
remove unused papers from bib
final for IRC3
v6.0 to PC
final from Ante's comments
to PC
fix figure1 and improved appendix11
6.2
final to IRC with appendix ?
add a reply
before You's comment
add a reference and correct wording
final for CR2
final version to CR2

\documentclass[ALICE,manyauthors]{cernphprep}

\usepackage[comma,square,numbers,sort&compress]{natbib}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{url,color}
\linenumbers

\begin{document}
%%%%%%%%%%%%% ptdr definitions %%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%  Title page %%%%%%%%%%%%%%%%%%%%%%%%
%
\newcommand{\PbPb}{\textnormal{Pb--Pb}}
\newcommand{\AuAu}{\textnormal{Au--Au}}
\newcommand{\tn}[1]{\textnormal{#1}}
\newcommand{\snn}{\ensuremath{\sqrt{s_\tn{NN}}}}
 % off by redefinding CKBNOTEje
\newcommand{\CKBNOTE}[1]{{\bf CKB:  #1}} 
\renewcommand{\CKBNOTE}[1]{}  % switch off

 % off by redefinding RHNOTE
\newcommand{\RHNOTE}[1]{{\bf RH:  #1}} 
\renewcommand{\RHNOTE}[1]{}  % switch off

\begin{titlepage}
%
\PHyear{2016}
\PHnumber{xxx}                 % required, obtained from PH
\PHdate{9 November}              % required, will be obtained from PH
%
%
%%% Put your own title + short title here:
\title{Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV}
\ShortTitle{Correlations between different order flow harmonics}   % appears on right page headers

@@

% \bibliographystyle{mybibstyle}
%\bibliographystyle{utphys}
%\bibliography{paper}
\bibliographystyle{utphys}
\bibliography{paper}

\newpage
%
%\input{}               %%%%%%%%%%% put your appendices here
%
%%%%%%%%% appendix with author list
\appendix
\section{The ALICE Collaboration}
\label{app:collab}
%\input{Alice_Authorlist_2015-Feb-18.tex}  %%%%%%% done by webmaster team
%\input{}              %%%%%%%%%%%% put the references here
%
\end{document}

>>>>

\documentclass[ALICE,manyauthors]{cernphprep}
\usepackage[comma,square,numbers,sort&compress]{natbib}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{url,color}
\usepackage{enumerate}   
%\usepackage{refcheck}
\linenumbers

\begin{document}
%%%%%%%%%%%%% ptdr definitions %%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%  Title page %%%%%%%%%%%%%%%%%%%%%%%%
%
\newcommand{\PbPb}{\textnormal{Pb--Pb}}
\newcommand{\AuAu}{\textnormal{Au--Au}}
\newcommand{\tn}[1]{\textnormal{#1}}
\newcommand{\snn}{\ensuremath{\sqrt{s_\tn{NN}}}}
\newcommand{\chisqndf}{\chi^2/N_{\rm dof}}
 % off by redefinding CKBNOTEje
\newcommand{\CKBNOTE}[1]{{\bf CKB:  #1}} 
\renewcommand{\CKBNOTE}[1]{}  % switch off

 % off by redefinding RHNOTE
\newcommand{\RHNOTE}[1]{{\bf RH:  #1}} 
\renewcommand{\RHNOTE}[1]{}  % switch off
\newcommand{\multfigsize}{0.95}
\begin{titlepage}
%
\PHyear{2017}
\PHnumber{xxx}                 % required, obtained from PH
\PHdate{21 August}              % required, will be obtained from PH
%
%
%%% Put your own title + short title here:
\title{Systematic studies of correlations between different order flow harmonics in Pb--Pb collisions at $\mathbf{\sqrt{s_{\rm NN}}}$ = 2.76 TeV}
\ShortTitle{Correlations between different order flow harmonics}   % appears on right page headers

@@

%\nocite{*}

% \bibliographystyle{mybibstyle}
%\bibliographystyle{utphys}
%\bibliography{paper}
\bibliographystyle{utphys}
\bibliography{paper.bib}
\newpage
%
%\input{}               %%%%%%%%%%% put your appendices here
\input{appendix.tex}
%
%%%%%%%%% appendix with author list
\section{The ALICE Collaboration}
\label{app:collab}
%\input{Alice_Authorlist_2015-Feb-18.tex}  %%%%%%% done by webmaster team
%\input{}              %%%%%%%%%%%% put the references here
%
\end{document}
